Impact of Satellite Constellations on the Legacy Survey of Space and Time

### 2022-09-28 ms.tex

However, one challenge for the LSST is that increasing numbers of bright
Low-Earth-Orbit (LEO) satellites (e.g., Starlink) are being launched, which could leave streaks
in astronomical pointings. Over the last three years, many astronomers have raised concerns
about the impact of this on the LEO ecosystem and astronomical surveys \citep{lawrence22,tyson20}. LEO satellites
are visible from Earth because they reflect sunlight, especially during twilight. As the
illuminated LEO satellites move across the field of view of an astronomical pointing, they leave
a streak in the image, which negatively impacts the scientific value of the pointing. Astronomers
predict there will be at least one satellite streaks in the majority of exposures of the Rubin
Observatory \citep{lawrence22}.An example of satellite streaks in an astronomical image is shown in Figure \ref{fig-streaks}.

\begin{figure}[ht!]\label{fig-streaks}
%\includegraphics{}  % preferably .eps
\caption{This is a caption}
\end{figure}

@@

\section{Methodology}
We begin by creating realistic forecasts of three different commercial satellite constellations: StarlinkV1 (4408 satellites, altitude 550 km), OneWeb (6372 satellites, altitude 550km), and StarlinkV2 (29988 satellites, altitude 550km). All three of these constellations are highly likely to launch as designed, or close to it, as both operators presently have functional satellites in orbit and are working to build and launch more. These simulated satellite
constellations are illustrated in Figure \ref{fig-simulated-constellations}.

\begin{figure}[ht!]\label{fig-simulated-constellations}
%\includegraphics{}  % preferably .eps
\caption{This is a caption}
\end{figure}

Using these simulated satellite constellations, we add an additional weighting for satellite
dodging to the Rubin Scheduler. Given an input satellite distribution, the scheduler predicts
satellite maps across a determined time frame. Based on the predicted location of satellites, the
scheduler creates a reward weighting: areas with more illuminated satellites will receive a more
negative reward weighting, or in other words, the scheduler is incentivized to avoid them. The
scheduler then combines the satellite reward weights with other weights to determine where to
point the telescope to take the next set of simulated observations. Figure \ref{fig-simulated-scheduler} shows an example of
scheduler weighting for the three simulated satellite constellations at two different sun altitudes.

\begin{figure}[ht!]\label{fig-simulated-scheduler}
%\includegraphics{}  % preferably .eps
\caption{This is a caption}
\end{figure}

@@

\begin{figure}[ht!]\label{fig-pixel-loss-weight}
%
%\includegraphics{}  % preferably .eps
\caption{This is a caption}
\end{figure}

@@

\begin{figure}[ht!]\label{fig-trade-off}
%\includegraphics{}  % preferably .eps
\caption{This is a caption}
\end{figure}

@@

\software{Astropy \citep{astropy2013, astropy2018}, 
          Healpy and HEALpix\footnote{\url{http://healpix.sourceforge.net}} \citep{healpix2005, Zonca2019},
          Matplotlib \citep{Hunter:2007},
          Numpy \citep{harris2020array},
          rubin\_sim \citep{yoachim2022},
          Scipy \citep{2020SciPy-NMeth},
          Shapely\footnote{https://github.com/shapely/shapely}}
          % todo: add citation to newest 2022 astropy paper

>>>>

However, one challenge for the LSST is that increasing numbers of bright
Low-Earth-Orbit (LEO) satellites (e.g., Starlink) are being launched, which could leave streaks
in astronomical pointings. Over the last three years, many astronomers have raised concerns
about the impact of this on the LEO ecosystem and astronomical surveys \citep{lawrence22,tyson20}. LEO satellites
are visible from Earth because they reflect sunlight, especially during twilight. As the
illuminated LEO satellites move across the field of view of an astronomical pointing, they leave
a streak in the image, which negatively impacts the scientific value of the pointing. Astronomers
predict there will be at least one satellite streaks in the majority of exposures of the Rubin
Observatory \citep{lawrence22}. % XXX-but, our results say OneWeb streaks 10% of Rubin images. We shouldn't repeat claims we know are wrong. And this is just citing tyson20, which does not say the majority of exposures would have a streak. 
An example of satellite streaks in an astronomical image is shown in Figure \ref{fig-streaks}.

\begin{figure}[ht!]
%\includegraphics{} 
\caption{Example image of a satellite streak \label{fig-streaks}}
\end{figure}

@@

\section{Methodology}
We begin by creating realistic forecasts of three different commercial satellite constellations: StarlinkV1 (4408 satellites, altitude 540-570 km), OneWeb (6372 satellites, altitude 1200 km), and StarlinkV2 (29988 satellites, altitude 340-614 km). All three of these constellations are highly likely to launch as designed (XXX-lol, no), or close to it, as both operators presently have functional satellites in orbit and are working to build and launch more. These simulated satellite
constellations are illustrated in Figure \ref{fig-simulated-constellations}.

\begin{figure}[ht!]
\epsscale{0.5}
%% XXX--ugh, so these have enough points that they take forever to render. Thoughts on how to improve welcome
%\plotone{plots/sats_slv1.pdf}
%\plotone{plots/sats_slv2.pdf}
%\plotone{plots/sats_ow.pdf}
\epsscale{1}
\caption{Hammer projection of the altitude and azimuth positions of our simulated satellite constellations as seen from Rubin Observatory on October 1, 2023 with a sun altitude of -18 degrees. Red points show un-illuminated satellites, blue points show those illuminated by the sun, and black points are illuminated and above the Rubin altitude limit. \label{fig-simulated-constellations}}
\end{figure}

Using these simulated satellite constellations, we add an additional weighting for satellite
dodging to the Rubin Scheduler. Given an input satellite distribution, the scheduler predicts
satellite maps across a determined time frame. Based on the predicted location of satellites, the
scheduler creates a reward weighting: areas with more illuminated satellites will receive a more
negative reward weighting, or in other words, the scheduler is incentivized to avoid them. The
scheduler then combines the satellite reward weights with other weights to determine where to
point the telescope to take the next set of simulated observations. Figure~\ref{fig-simulated-scheduler} shows an example of
scheduler weighting for the three simulated satellite constellations at two different sun altitudes.

XXX--quantify the basis function maps a bit more. The positions of the illuminated satellites are computed in 10s intervals. These maps are then summed over 90 minute blocks to generate an avoidance map.

\begin{figure}[ht!]
%\includegraphics{}  % preferably .eps
\caption{Example of satellite avoidance maps. \label{fig-simulated-scheduler}}
\end{figure}

@@

\begin{figure}[ht!]
%
%\includegraphics{}  % preferably .eps
\caption{Pixels lost as a function of satellite dodging weight. \label{fig-pixel-loss-weight}}
\end{figure}

@@

\begin{figure}[ht!]
%\includegraphics{}  % preferably .eps
\caption{Pixel loss vs coadded depth. \label{fig-trade-off}}
\end{figure}

@@

\software{Astropy \citep{astropy2013, astropy2018}, 
          Healpy and HEALpix\footnote{\url{http://healpix.sourceforge.net}} \citep{healpix2005, Zonca2019},
          Matplotlib \citep{Hunter:2007},
          Numpy \citep{harris2020array},
          rubin\_sim \citep{yoachim2022},
          Scipy \citep{2020SciPy-NMeth},
          Skyfield \citep{Rhodes2019}, 
          Shapely \citep{shapely2007}}
          % todo: add citation to newest 2022 astropy paper
